### 2011-05-06 paper/paper.tex
made change to conclusion
more minor edits

Thus, the transition functions are symmetric, so by \ref{symmetric}, both ball-walking and Gaussian-walking have a stationary uniform distribution.
\end{proof}

@@

We implemented separation oracles for a cube, a sphere, and a simplex for dimensions and tested the algorithms for dimensions $n\in\{2,3,4,7,10,100\}$.
\begin{itemize}
\item \emph{The cube.} This is simply the region $(-1,1)^n$.
\item \emph{The sphere.} This is simply the region $\{(x_1,...,x_n)\in\mathbb{R}^n : x_1^2 + x_2^2 + \cdots + x_n^2 < 1\}$.
\item \emph{The simplex.} We defined this as the interior of the convex hull of the points $e_1, ..., e_n$ (defined by $e_{i,j} = 1$ if $i=j$ and $e_{i,j} = 0$ otherwise) and $f = (c,c,...,c)$ where\linebreak $c = (1 - \sqrt{n + 1}) / n$. We can compute that any two of these $n+1$ points are of Euclidean distance $\sqrt{2}$ from each other. To test if a point $p$ lies inside the simplex, we draw a line through $f$ and $p$, and intersect it with the plane $x_1 + x_2 + \cdots + x_n = 1$, say this intersection is $q$. First, we want to check that $p$ lies between $f$ and $q$. If so, then we just need to check that $q$ lies in the convex hull of $e_1,e_2,...,e_n$, but this is equivalent to checking that each coordinate of $q$ is nonnegative.
\end{itemize}

@@

In conclusion, we have found that the results of our tests confirm what we thought to be theoretically true: the hit-and-run method performs much better than the Metropolis methods. With a good start, hit-and-run required only something on the order of $1000$ iterations to produce a distribution that seemed reasonably uniform, which is even better than the bound given in \ref{hitandrunbound}, even with $100$ dimensions, whereas this cube is too larger for the the basic-ball walking method to have a good chance of even reaching the edges. We also saw that the basic Gaussian-walking method worked better than the ball-walking method in this case.

In general, the adaptive methods performed better than their non-adaptive counterparts. When started from the corner of a cube or a simplex, the non-adaptive methods would always stay in that corner for high-dimension test cases, even $n=10$. The adaptive methods, however, produced a distribution which looked much more uniform.

>>>>

Thus, the transition functions are symmetric, so by Theorem \ref{symmetric}, both ball-walking and Gaussian-walking have a stationary uniform distribution.
\end{proof}

@@

We implemented separation oracles for a cube, a sphere, and a simplex for dimensions and tested the algorithms for dimensions $n\in\{2,3,4,7,10,100\}$.
\begin{itemize}
\item \emph{The cube.} This is simply the region $(-1,1)^n$.
\item \emph{The sphere.} This is simply the region $\{(x_1,...,x_n)\in\mathbb{R}^n : x_1^2 + x_2^2 + \cdots + x_n^2 < 1\}$.
\item \emph{The simplex.} We defined this as the interior of the convex hull of the points $e_1, ..., e_n$ (which are defined by $e_{i,j} = 1$ if $i=j$ and $e_{i,j} = 0$ otherwise) and $f = (c,c,...,c)$ where\linebreak $c = (1 - \sqrt{n + 1}) / n$. We can compute that any two of these $n+1$ points are of Euclidean distance $\sqrt{2}$ from each other. To test if a point $p$ lies inside the simplex, we draw a line through $f$ and $p$, and intersect it with the plane $x_1 + x_2 + \cdots + x_n = 1$, say this intersection is $q$. First, we want to check that $p$ lies between $f$ and $q$. If so, then we just need to check that $q$ lies in the convex hull of $e_1,e_2,...,e_n$, but this is equivalent to checking that each coordinate of $q$ is nonnegative.
\end{itemize}

@@

In conclusion, we have found that the results of our tests confirm what we thought to be theoretically true: the hit-and-run method performs much better than the Metropolis methods. With a good start, hit-and-run required only something on the order of $1000$ iterations to produce a distribution that seemed reasonably uniform, which is even better than the bound given in Theorem \ref{hitandrunbound}, even with $100$ dimensions, whereas this cube is too larger for the the basic-ball walking method to have a good chance of even reaching the edges. We also saw that the basic Gaussian-walking method worked better than the ball-walking method in this case.

In general, the adaptive methods performed better than their non-adaptive counterparts. When started from the corner of a cube or a simplex, the non-adaptive methods would always stay in that corner for high-dimension test cases, even $n=10$. The adaptive methods, however, produced a distribution which looked much more uniform. However, in cases where we do not start close to a boundary, the adaptive methods do not have as much of an advantage over the non-adaptive methods.
